Supplemental Material: Multidimensional analysis and detection of informative features in human brain white matter

### 2021-04-20 reports/manuscript/paper.tex
Small wording change.

The present work aims to balance predictive accuracy with descriptive power
\cite{Murdoch2019-ax, Breiman2001-uz} by capitalizing on all of the available
data across all bundles, while also retaining and elucidating spatial
information about the locations that are most informative for discriminative
performance.
Unlike many previous analyses of white matter (e.g., using TBSS \cite{smith2006tract} and connectometry \cite{yeh2016connectometry}), which focus on classical inference of the differences between groups or individuals in terms of their white matter properties, the focus of the present work is on the combination of features that facilitate accurate prediction of the individual differences in a \emph{phenotype}.
For example, an accurate prediction of which individuals in a group have a particular disease, or a prediction of their age with small error. The distinct goals of \emph{inference} and \emph{prediction} are not necessarily incongruent, but can sometimes be in tension \cite{Bzdok2020-sd}. This distinction is also similar to the distinction between ``encoding'' and ``decoding'' used in the functional MRI literature \cite{Naselaris2011-ss}. In the present work, we predict the phenotypical variance in a group of subjects (or classify group membership), based on a linear combination of the features estimated with tract profiling.

>>>>

The present work aims to balance predictive accuracy with descriptive power
\cite{Murdoch2019-ax, Breiman2001-uz} by capitalizing on all of the available
data across all bundles, while also retaining and elucidating spatial
information about the locations that are most informative for discriminative
performance.
Unlike many previous analyses of white matter (e.g., using TBSS \cite{smith2006tract} and connectometry \cite{yeh2016connectometry}), which focus on classical inference about the differences between groups or individuals in terms of their white matter properties, the focus of the present work is on the combination of features that facilitate accurate prediction of the individual differences in a particular phenotype.
For example, an accurate prediction of which individuals in a group have a particular disease, or a prediction of their age with small error. The distinct goals of \emph{inference} and \emph{prediction} are not necessarily incongruent, but can sometimes be in tension \cite{Bzdok2020-sd}. This distinction is also similar to the distinction between ``encoding'' and ``decoding'' used in the functional MRI literature \cite{Naselaris2011-ss}. In the present work, we predict the phenotypical variance in a group of subjects,or classify group membership, based on a linear combination of the features estimated with tract profiling.

### 2021-04-20 reports/manuscript/paper_changes.tex
Small wording change.

The present work aims to balance predictive accuracy with descriptive power
\cite{Murdoch2019-ax, Breiman2001-uz} by capitalizing on all of the available
data across all bundles, while also retaining and elucidating spatial
information about the locations that are most informative for discriminative
performance.
\added{Unlike many previous analyses of white matter (e.g., using TBSS \cite{smith2006tract} and connectometry \cite{yeh2016connectometry}), which focus on classical inference of the differences between groups or individuals in terms of their white matter properties, the focus of the present work is on the combination of features that facilitate accurate prediction of the individual differences in a \emph{phenotype}}.
\added{For example, an accurate prediction of which individuals in a group have a particular disease, or a prediction of their age with small error. The distinct goals of \emph{inference} and \emph{prediction} are not necessarily incongruent, but can sometimes be in tension \cite{Bzdok2020-sd}. This distinction is also similar to the distinction between ``encoding'' and ``decoding'' used in the functional MRI literature \cite{Naselaris2011-ss}. In the present work}, we predict the phenotypical variance in a group of subjects (or classify group membership), based on a linear combination of the features estimated with \replaced{tract profiling}{tractometry}.

>>>>

The present work aims to balance predictive accuracy with descriptive power
\cite{Murdoch2019-ax, Breiman2001-uz} by capitalizing on all of the available
data across all bundles, while also retaining and elucidating spatial
information about the locations that are most informative for discriminative
performance.
\added{Unlike many previous analyses of white matter (e.g., using TBSS \cite{smith2006tract} and connectometry \cite{yeh2016connectometry}), which focus on classical inference about the differences between groups or individuals in terms of their white matter properties, the focus of the present work is on the combination of features that facilitate accurate prediction of the individual differences in a particular phenotype}.
\added{For example, an accurate prediction of which individuals in a group have a particular disease, or a prediction of their age with small error. The distinct goals of \emph{inference} and \emph{prediction} are not necessarily incongruent, but can sometimes be in tension \cite{Bzdok2020-sd}. This distinction is also similar to the distinction between ``encoding'' and ``decoding'' used in the functional MRI literature \cite{Naselaris2011-ss}. In the present work}, we predict the phenotypical variance in a group of subjects,or classify group membership, based on a linear combination of the features estimated with \replaced{tract profiling}{tractometry}.
